---
title: "Capstone project"
output: html_notebook
---

Import batting dataset

```{r}
batting <- read.csv("datasets/Batting.csv", stringsAsFactors = T)
```

Check head

```{r}
head(batting)
```

Check the structure of dataset

```{r}
str(batting)
```

```{r}
summary(batting)
```

```{r}
head(batting$AB)
```

```{r}
head(batting$X2B)
```

```{r}
batting$BA <- batting$H/batting$AB
```

```{r}
tail(batting$BA, 5)
```

Create a new column, 1B (Singles)

```{r}
batting$X1B <- batting$H - batting$X2B - batting$X3B - batting$HR
```

Create a new column, OBP (On-base percentage)

```{r}
batting$OBP <- (batting$H + batting$BB + batting$HBP)/(batting$AB + batting$BB + batting$HBP + batting$SF)
```

Create a new column, SLG (Slugging percentage)

```{r}
batting$SLG <- (batting$X1B + (2 * batting$X2B) + (3 * batting$X3B) + (4 * batting$HR))/batting$AB
```

```{r}
str(batting)
```

Import salaries dataset

```{r}
sal <- read.csv("datasets/Salaries.csv", stringsAsFactors = T)
```

```{r}
summary(sal)
```

```{r}
summary(batting)
```

```{r}
batting <- subset(batting, yearID >= 1985)
```

```{r}
summary(batting)
```

```{r}
combo <- merge(batting, sal, by = c("playerID", "yearID"))
```

```{r}
summary(combo)
```

```{r}
lost_players <- subset(combo, playerID %in% c("giambja01", "damonjo01", "saenzol01"))
lost_players
```

```{r}
lp_2001 <- subset(lost_players, yearID == 2001)
col <- c("playerID", "H", "X2B", "X3B", "HR", "OBP", "SLG", "BA", "AB")
lp_2001 <- lp_2001[, col]
lp_2001
```

```{r}
head(lost_players)
```

## **Replacement Players**

Now we have all the information we need! Here is your final task - Find Replacement Players for the key three players we lost! However, you have three constraints:

-   The total combined salary of the three players can not exceed 15 million dollars.

-   Their combined number of At Bats (AB) needs to be equal to or greater than the lost players.

-   Their mean OBP had to equal to or greater than the mean OBP of the lost players

```{r}
lp_total_AB <- sum(lp_2001$AB)
lp_total_AB
```

```{r}
max_salary <- 15000000
max_salary
```

```{r}
lp_avg_OBP <- mean(lp_2001$OBP)
lp_avg_OBP
```

```{r}
combo_2001 <- subset(combo, yearID == 2001 & OBP > 0)
str(combo_2001)
```

```{r}
combo_2001 <- subset(combo_2001, AB >= lp_total_AB/3 & salary < max_salary/3 & OBP >= lp_avg_OBP)
str(combo_2001)
```

```{r}
library(dplyr)
```

```{r}
options <- arrange(combo_2001, desc(OBP))
options[, c("playerID", "OBP", "AB", "salary")]
```
